### 2019-05-22 thesis-template/msc-thesis.tex
update
add

\textbf{Symmetric Tensor Field Visualization}\\
\cite{pang&zheng} et.al. proposed a texture-based visualization approach called HyperLIC, which extends the concept of LIC to symmetric tensor fields by using an anisotropic 2D-filter kernel oriented along the major/minor eigenvectors. The concept of following the major/minor eigenvector along tensor field lines was invented by \cite{vilanova}. Tensorlines introduce a kind of artificial inertia (running average), making them resistent to noise. The notion of tensor field topology and the concept of Hyperstreamlines was first introduced by \cite{delmarcelle&hesselink}. The placement of tensor field lines as hyperstreamlines was recently improved by \cite{spencer} et.al. for glyph packing. A good overview of seeding strategies is given by \cite{mcloughlin}. \cite{feng} et. al. used Voronoi Tesselation for placing the glyphs. Superquadric glyphs have been proposed by \cite{schultz&kindlmann} for general (non-positive definite) tensors. \cite{deleeuw&vanwijk} visualize the partial derivative gradient, the Jacobian of the tensor field to sense the local properties of the field. A diffusion tensor can also be visualized by box, ellipsoid \cite{pierpaoli}, composite \cite{worth} or superquadric \cite{kindlmann} glyphs. There is also a set of scalar measures available in symmetric tensor field visualization such as: mean diffusivity, fractional anisotropy \cite{basser} and anisotropy coefficients \cite{westin}.
\\
\textbf{Asymmetric Tensor Field Visualization}\\
\cite{pang&zheng} et.al. proposed the concept of dual eigenvectors and \cite{zhang} extended it to pseudo-eigenvectors and introduced the eigenvector/eigenvalue manifolds to visualize eigenvectors in the complex domain. \cite{laramee} et.al. focused on the efficient implementation and visualization of these structures and provided an interactive visualization system for asymmetric tensors applicable in fluid and solid dynamics. The concept of Tensor Magnitude has been introduced by \cite{laramee2} for means of physical interpretation. They also proposed an efficient glyph and hyperstreamline hybrid approach, which made dynamic interaction in real-time in 2D tensor fields feasible. \cite{palacios} extracted isosurfaces of tensor magnitude, mode and isotropy index.

@@

\section{Global Illumination Scheme}
\label{sec:scheme}
Within the scope of this work, we will develop a Global Illumination Scheme designed to efficiently propagate the intensities stored in discrete polar coordinates given as impulses (stimuli) by the user or the config. Polar profiles for different light sources are shown in Fig. \ref{polar}:
\begin{figure}[h]
  \centering
 {
    \includegraphics[width=0.8\textwidth]
    {img/scheme2.png}
  }
  \caption{Propagation Scheme}
  \label{polar}
\end{figure}\vskip 3pt
Polar profiles map each angle $\varphi$ a magnitude $\hat{r}$ forming a function $\hat{r}(\varphi)$. They are circular axis versions of the domain $[0..2\pi]$, with negative magnitudes mirrored by 180 degrees). In the sense of interpretability, we exclude negative values (energies) from the scope of our calculations. As a start-up for the propagation, we will think of a grid cell in 2D as a center pixel within an 8-neighborhood. It has 8 (4 faces/edges and 4 diagonals) unique neighbors, which are adjacent point lights in the grid (the type of light source with theoretically no finite extend). We consider one face neighbor (top) to shortly explain the steps of the scheme. The diagonals and the others are obtained from derivation and symmetry.

@@

We place a cosine lobe scaled with the integrated energies in each of the 8 cone directions, whereas outgoing integrated and summed energies are weighted by the linear combination weights (factors) in overlapping (green) areas to split up the contributions accordingly. The contribution areas are depicted in Fig. \ref{scheme}, the cosine lobes can be observed in Fig. \ref{iter} respectively. This manner of propagation is inspired by the propagation scheme of \cite{dachsbacher} et.al. (see the paper on how to "project the flux into a point light"). The implementation is done in a dual buffer approach which pushes the energies back and forth (buffer A to buffer B) until convergence, which happens when the energy is spreaded throughout the grid and enters a stationary state, characterized by equal out (at grid borders) to in (at light source positions) energy-flow with no more nettings going on inside the domain. Note that even though we propagate the energy directly through the diagonal cones (which forms a square initially), the 8 degrees of freedom introduce a circular (spherical) wave front after few iterations (for greater resolutions). This occurs, since the diagonals are more strongly attenuated by default and there is a redistribution of intensities in the long term resulting in a circular torus-shaped distribution, as depicted in Fig. \ref{iter}. Also note, that this approach satisfies energy conservation and propagation attenuation principles and applies to the principles of light propagation in vacuum (by default). The verification of these principal requirements and specifications can be observed in the Experimental Evaluation in chap. \ref{chap:eval}.

@@

At last, we define a threshold for the minimum overall distribution error taken into account for convergence conditions, initiating a stop sequence when falling below that threshold. As already mentioned, a dual-buffer approach is chosen here, as we can efficiently propagate from one into the other and just swap pointers to 
start all over (after reinitialization) and also since it yields a reasonable source-target structure. Until now we aimed to simulate the propagation of light in empty space (vacuum) providing us with a physically-motivated base-approach. We aim to modulate the transmission of the energies on top of the base approach with transmission profiles obtained from the tensor fields through Principal Component Analysis in the following.

>>>>

\textbf{Symmetric Tensor Field Visualization}\\
\cite{pang&zheng} et.al. proposed a texture-based visualization approach called HyperLIC, which extends the concept of LIC to symmetric tensor fields by using an anisotropic 2D-filter kernel oriented along the major/minor eigenvectors. The concept of following the major/minor eigenvector along tensor field lines was invented by \cite{vilanova}. Tensorlines introduce a kind of artificial inertia (running average), making them resistent to noise. The notion of tensor field topology and the concept of Hyperstreamlines was first introduced by \cite{delmarcelle&hesselink}. The placement of tensor field lines as hyperstreamlines was recently improved by \cite{spencer} et.al. for glyph packing. A good overview of seeding strategies is given by \cite{mcloughlin}. \cite{feng} et. al. used Voronoi Tesselation for placing the glyphs. Superquadric glyphs have been proposed by \cite{schultz&kindlmann} for general (non-positive definite) tensors. \cite{deleeuw&vanwijk} visualize the partial derivative gradient, the Jacobian of the tensor field to sense the local properties of the field. A diffusion tensor can also be visualized by box \cite{makris}, ellipsoid \cite{pierpaoli}, composite \cite{worth} or superquadric \cite{kindlmann} glyphs. There is also a set of scalar measures available in symmetric tensor field visualization such as: mean diffusivity, fractional anisotropy \cite{basser} and anisotropy coefficients \cite{westin}. \cite{hlawatsch} et.al. obtain a coordinate (flow) map from tensor field lines following major/minor eigenvectors (fibre trajectories) and use the spectral norm of the Cauchy-Green deformation tensor to compute the FTLE-field in homogeneous regions. In a similar manner, we opt to use Global Illumination Techniques to obtain a light distribution footprinted (in form of weighting profiles obtained from ellipsoid glyphs) by the tensor field.
\\
\textbf{Asymmetric Tensor Field Visualization}\\
\cite{pang&zheng} et.al. proposed the concept of dual eigenvectors and \cite{zhang} extended it to pseudo-eigenvectors and introduced the eigenvector/eigenvalue manifolds to visualize eigenvectors in the complex domain. \cite{laramee} et.al. focused on the efficient implementation and visualization of these structures and provided an interactive visualization system for asymmetric tensors applicable in fluid and solid dynamics. The concept of Tensor Magnitude has been introduced by \cite{laramee2} for means of physical interpretation. They also proposed an efficient glyph and hyperstreamline hybrid approach, which made dynamic interaction in real-time in 2D tensor fields feasible. \cite{palacios} extracted isosurfaces of tensor magnitude, mode and isotropy index.

@@

\section{Global Illumination Scheme}
\label{sec:scheme}
Within the scope of this work, we will develop a Global Illumination Scheme designed to efficiently propagate the intensities stored in discrete polar coordinates given as impulses (stimuli) by the user or the config. Polar profiles for different light sources are shown in Fig. \ref{polar}:
\begin{figure}[h]
  \centering
 {
    \includegraphics[width=0.8\textwidth]
    {img/strahler.png}
  }
  \caption{Types of Emitters}
  \label{polar}
\end{figure}\vskip 3pt
Polar profiles map each angle $\varphi$ a magnitude $\hat{r}$ forming a function $\hat{r}(\varphi)$. They are circular axis versions of the domain $[0..2\pi]$, with negative magnitudes mirrored by 180 degrees). In the sense of interpretability, we exclude negative values (energies) from the scope of our calculations. As a start-up for the propagation, we will think of a grid cell in 2D as a center pixel within an 8-neighborhood. It has 8 (4 faces/edges and 4 diagonals) unique neighbors, which are adjacent point lights in the grid (the type of light source with theoretically no finite extend). We consider one face neighbor (top) to shortly explain the steps of the scheme. The diagonals and the others are obtained from derivation and symmetry.

@@

We place a cosine lobe scaled with the integrated (accumulated) energies in each of the 8 cone directions, whereas outgoing integrated and summed energies are weighted by the linear combination weights (factors) in overlapping (green) areas to split up the contributions accordingly. The contribution areas are depicted in Fig. \ref{scheme}, the cosine lobes can be observed in Fig. \ref{iter} respectively. This manner of propagation is inspired by the propagation scheme of \cite{dachsbacher} et.al. (see the paper on how to "project the flux into a point light"). The implementation is done in a dual buffer approach which pushes the energies back and forth (buffer A to buffer B) until convergence, which happens when the energy is spreaded throughout the grid and enters a stationary state, characterized by equal out (at grid borders) to in (at light source positions) energy-flow with no more nettings going on inside the domain. Note that even though we propagate the energy directly through the diagonal cones (which forms a square initially), the 8 degrees of freedom introduce a circular (spherical) wave front after few iterations (for greater resolutions). This occurs, since the diagonals are more strongly attenuated by default and there is a redistribution of intensities in the long term resulting in a circular torus-shaped distribution, as depicted in Fig. \ref{iter}. Also note, that this approach satisfies energy conservation and propagation attenuation principles and applies to the principles of light propagation in vacuum (by default). The verification of these principal requirements and specifications can be observed in the Experimental Evaluation in chap. \ref{chap:eval}.

@@

At last, we define a threshold for the minimum overall distribution error taken into account for convergence conditions, initiating a stop sequence when falling below that threshold. As already mentioned, a dual-buffer approach is chosen here, as we can efficiently propagate from one into the other and just swap pointers to 
start all over (after reinitialization). Another reason is it yields a reasonable source-target structure. Until now, we aimed to simulate the propagation of light in empty space (vacuum) providing us with a physically-motivated but very simplified base-approach. We aim to modulate the transmission of the energies on top of the base approach with transmission profiles obtained from the tensor fields through Principal Component Analysis and ellipsoid glyph equations in the following.
